Filling in the Gaps: Using Consumer Products to Replace Missing Pollution Data

### 2022-03-07 paper/15min-presentation/15min-presentation.tex
Updates from Overleaf

%---------------------------------------------------------
%Results: Sample EPA Sites
\begin{frame}
\frametitle{Results for Daily Design Value: Sample EPA Sites}
\includegraphics[width=\textwidth]{output/figures/final_results/DV_plot_all_test_sites.png}
\end{frame}
%---------------------------------------------------------

@@

\includegraphics[width=\textwidth]{output/figures/final_results/DV_plot_site_019-0500.png}

@@

%---------------------------------------------------------
%Results: Sample EPA Sites
\begin{frame}
\frametitle{Results for 24-hour Design Value: Sample EPA Sites}
\includegraphics[width=\textwidth]{output/figures/final_results/DV}
\end{frame}
%---------------------------------------------------------

\includegraphics[width=\textwidth]{output/figures/final_results/DV_plot_site_019-0500.png}

%---------------------------------------------------------
%Conclusions & Discussion
\begin{frame}
\frametitle{Conclusions \& Discussion}
\begin{enumerate}
    \item Most sites tested show little evidence of bias from missing data, but some have large, meaningful bias
\end{enumerate}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Future Work
\begin{frame}
\frametitle{Future Work}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
% Purple Air EPA Correction
\begin{frame}
\frametitle{Correction of PurpleAir Readings}
$$
\widetilde{PA}_{j,t}=\begin{cases}
			0.52*PA_{j,t} - 0.086*H_{j,t} + 5.75, & \text{if $PA_{j,t} \leq 343 \mu$g/m$^3$}\\
            0.46*PA_{j,t} + 0.(3.93e-4)PA_{j,t}^2 + 2.97, & \text{otherwise}
		 \end{cases}
$$
\begin{itemize}
    \item $PA_{j,t}$ = ambient PM2.5 measured by PurpleAir sensor $j$ at time $t$
    \item $H_{j,t}\in[0,1]$ is the relative humidity
\end{itemize}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
% Future Prediction Equation
\begin{frame}
\frametitle{Better Prediction of EPA PM2.5}

@@

%---------------------------------------------------------
% Fresno Site Data
\begin{frame}
\frametitle{Fresno Site Data}

@@

%---------------------------------------------------------
%Extra Tables
\begin{frame}
\frametitle{Table: Fresno, California}

\begin{table}[]
\caption{Design Value Comparison for Fresno, CA. (98\% CI Bounds)}
\label{tab:fresno_dvs}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}l|lll|lll@{}}
Year-Quarter & \begin{tabular}[c]{@{}l@{}}Annual DV\\ Difference\end{tabular} & \begin{tabular}[c]{@{}l@{}}Upper \\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Lower\\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hour DV \\ Difference\end{tabular} & \begin{tabular}[c]{@{}l@{}}Upper \\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Lower \\ Bound\end{tabular} \\ \midrule
2018-4 & Invalid DV &  &  & Invalid DV &  &  \\
2019-1 & -0.005 & 0.133 & -0.143 & 0.000 & 0.252 & 0.000 \\
2019-2 & -0.003 & 0.141 & -0.147 & 0.000 & 0.252 & 0.000 \\
2019-3 & 0.015 & 0.170 & -0.139 & 0.058 & 2.202 & 0.000 \\
2019-4 & 0.002 & 0.190 & -0.185 & 0.000 & 1.460 & -0.024 \\
2020-1 & -0.012 & 0.182 & -0.207 & 0.000 & 0.335 & 0.000 \\
2020-2 & -0.010 & 0.191 & -0.211 & 0.000 & 0.376 & 0.000 \\
2020-3 & 0.679 & 0.954 & 0.403 & 8.718 & 11.704 & 8.556 \\
2020-4 & 0.647 & 1.006 & 0.288 & 5.979 & 8.281 & 5.851 \\
2021-1 & 0.564 & 1.036 & 0.091 & 3.007 & 4.184 & 2.903 \\
2021-2 & 0.533 & 1.024 & 0.042 & 3.007 & 4.225 & 2.903 \\
2021-3 & 0.630 & 1.129 & 0.132 & 7.607 & 10.557 & 7.444
\end{tabular}%
}
\end{table}
\end{frame}
%---------------------------------------------------------

>>>>

%---------------------------------------------------------
%Results: Sample EPA Sites
\begin{frame}
\frametitle{Results for Daily Design Value: Sample EPA Sites}
\includegraphics[width=\textwidth]{output/figures/final_results/DV_annual_plot_all_test_sites.png}

{\small Shaded regions are 95\% confidence intervals from interpolating the data.}
\end{frame}
%---------------------------------------------------------

@@

\includegraphics[width=\textwidth]{output/figures/final_results/DV_annual_plot_site_019-0500.png}

{\small Shaded regions are 95\% confidence intervals from interpolating the data.}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Results: Sample EPA Sites
\begin{frame}
\frametitle{Results for 24-hour Design Value: Sample EPA Sites}
\includegraphics[width=\textwidth]{output/figures/final_results/DV_hour_plot_all_test_sites.png}

{\small Shaded regions are 95\% confidence intervals from interpolating the data.}
\end{frame}
%---------------------------------------------------------

\includegraphics[width=\textwidth]{output/figures/final_results/DV_hour_plot_site_019-0500.png}

{\small Shaded regions are 95\% confidence intervals from interpolating the data.}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Conclusions & Discussion
\begin{frame}
\frametitle{Conclusions \& Discussion}
\begin{enumerate}
\setlength\itemsep{2em}
    \item Most tested sites show little evidence of bias from missing data, but one has large, meaningful bias
    \item Even one site can affect millions of people due to the sparsity of monitoring sites
    \item As high-pollution locations continue to reduce pollution, this bias may play an important role in determining NAAQS compliance
    \item Underlines importance of expanding the monitor network or exploring alternative measures of ambient air quality
\end{enumerate}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Future Work
\begin{frame}
\frametitle{Future Work}

\begin{itemize}
\setlength\itemsep{2em}
    \item Optimal regulation of ambient pollution under monitor expense-accuracy tradeoff
    \item Expand test to rest of US monitors
    \item Explore spatial distribution of air quality in unmonitored locations
\end{itemize}

@@

%---------------------------------------------------------
% Purple Air EPA Correction
\begin{frame}
\frametitle{Appendix: Correction of PurpleAir Readings}
$$
\widetilde{PA}_{j,t}=\begin{cases}
			0.52*PA_{j,t} - 0.086*H_{j,t} + 5.75, & \text{if $PA_{j,t} \leq 343 \mu$g/m$^3$}\\
            0.46*PA_{j,t} + 0.(3.93e-4)PA_{j,t}^2 + 2.97, & \text{otherwise}
		 \end{cases}
$$
\begin{itemize}
    \item $PA_{j,t}$ = ambient PM2.5 measured by PurpleAir sensor $j$ at time $t$
    \item $H_{j,t}\in[0,1]$ is the relative humidity
\end{itemize}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
% Future Prediction Equation
\begin{frame}
\frametitle{Appendix: Better Prediction of EPA PM2.5}

@@

%---------------------------------------------------------
% Fresno Site Data
\begin{frame}
\frametitle{Appendix: Fresno Site Data}

@@

%---------------------------------------------------------
%Extra Tables
\begin{frame}
\frametitle{Appendix: Fresno, California DV Bias Table}
\vspace{-1em}
\begin{table}[]
\caption{Design Value Comparison for Fresno, CA. (95\% CI Bounds)}
\label{tab:fresno_dvs}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}l|lll|lll@{}}
Year-Quarter & \begin{tabular}[c]{@{}l@{}}Annual DV\\ Difference\end{tabular} & \begin{tabular}[c]{@{}l@{}}Upper \\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Lower\\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hour DV \\ Difference\end{tabular} & \begin{tabular}[c]{@{}l@{}}Upper \\ Bound\end{tabular} & \begin{tabular}[c]{@{}l@{}}Lower \\ Bound\end{tabular} \\ \midrule
2018-4 & Invalid DV &  &  & Invalid DV &  &  \\
2019-1 & -0.005 & 0.133 & -0.143 & 0.000 & 0.252 & 0.000 \\
2019-2 & -0.003 & 0.141 & -0.147 & 0.000 & 0.252 & 0.000 \\
2019-3 & 0.015 & 0.170 & -0.139 & 0.058 & 2.202 & 0.000 \\
2019-4 & 0.002 & 0.190 & -0.185 & 0.000 & 1.460 & -0.024 \\
2020-1 & -0.012 & 0.182 & -0.207 & 0.000 & 0.335 & 0.000 \\
2020-2 & -0.010 & 0.191 & -0.211 & 0.000 & 0.376 & 0.000 \\
2020-3 & 0.679 & 0.954 & 0.403 & 8.718 & 11.704 & 8.556 \\
2020-4 & 0.647 & 1.006 & 0.288 & 5.979 & 8.281 & 5.851 \\
2021-1 & 0.564 & 1.036 & 0.091 & 3.007 & 4.184 & 2.903 \\
2021-2 & 0.533 & 1.024 & 0.042 & 3.007 & 4.225 & 2.903 \\
2021-3 & 0.630 & 1.129 & 0.132 & 7.607 & 10.557 & 7.444
\end{tabular}%
}
\end{table}
\end{frame}
%---------------------------------------------------------
